Efficient Machine Learning in a Memristor Network

### 2025-04-03 paper/paper.tex
Increases test error points

We broaden the training capability of the network by including a linear regression task, where, in its simplest form, the network is trained to give potential output $V^{\text{out}}$ related to the input potential $V^{\text{in}}$ via a linear relationship
\begin{equation}
    V_{\text{out}} = \text{a} V_{\text{in}} + \text{b}.
\label{eq:linear_relationship}
\end{equation}
We generate two sets of data, a training test $\{ V_{\text{in}}, V_{\text{out}} }_{i=1}^{}$

>>>>

We broaden the training capability of the network by including a linear regression task, where, in its simplest form, the network is trained to give potential output $V^{\text{out}}$ related to the input potential $V^{\text{in}}$ via a linear relationship
\begin{equation}
    V_{\text{out}} = \text{a} V_{\text{in}} + \text{b}.
\label{eq:linear_relationship}
\end{equation}
We generate two sets of data, a training test $ \{ V_{\text{in}}, V_{\text{out}} \}_{i=1}^{T}$ and a test set $\{ V_{\text{in}}, V_{\text{out}} \}_{i=1}^{Te}$. To create the test set, a random number in the interval $[1V, 4V]$ is created and fed to equation \cref{eq:linear_relationship}, giving a set of outputs that satifiy the desired relationship. At each step of the training algorithm above presented, a pair of input and output voltages is selected from the training set, and used
